Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-07-26 snapshot_system/abs.tex

\begin{abstract}
A cloud environment that  hosts a large number of  virtual machines (VMs) has
a high storage demand for frequent backup of system image snapshots.
Deduplication of data blocks can lead a big reduction of redundant blocks when
their signatures are identical. However it is expensive and less fault-resilient to perform a global deduplication
using signatures and let a data block share by many virtual machines. 
This paper studies a VM-centric scheme which collocates a lightweight
backup service with other cloud services in a cluster and it integrates multiple duplicate detection strategies 
that  localize deduplication as much as possible within each virtual machine.
It also organizes the write of small data chunks into large file system blocks so
that each underlying file block is associated with one VM for most of cases.
Our analysis shows that  this VM centric scheme 
can  provide  better fault tolerance while using a small amount of computing and storage resource. 
This  paper  provides a comparative evaluation of this scheme in  accomplishing a high deduplication 
efficiency while sustaining a good backup throughput.

>>>>

\begin{abstract}
A cloud environment that  hosts a large number of  virtual machines (VMs) has
a high storage demand for frequent backup of system image snapshots and
signature-based deduplication of data blocks is necessary to eliminate excessive 
redundant blocks.  Collocating a cluster-based duplicate service with other cloud services
reduces network traffic;
% when their signatures are identical. 
however it is resource expensive and less fault-resilient to perform a global deduplication
and let a data block share by many virtual machines. 
This paper proposes a VM-centric collocated backup service that  
localizes deduplication as much as possible within each virtual machine
and associates  underlying file blocks with one VM for most of cases.
Our analysis shows that  this VM centric scheme 
can  provide  better fault tolerance while using a small amount of computing and storage resource. 
This  paper  describes a comparative evaluation of this scheme in  accomplishing a high deduplication 
efficiency while sustaining a good backup throughput.

### 2013-07-26 snapshot_system/eval1.tex

>>>>

\subsection{Impact on Fault Tolerance}

Figure~\ref{fig:vm-availability} shows the reliability of VM backups as storage
nodes fail for different amounts of sharing of filesystem blocks in the index. We
show 5 and 20 for the VO and VC block links counts because those are what we
measured in our small dataset, and chose higher numbers to account for much
larger datasets. We chose to use a very optimistic setting for VO (20), and the
absolute worst case amount of sharing for VC in a 100 machine cluster with 25
VMs per machine (2500). Our results show that even the VC worst case provides
better VM reliability that VO. As you can see from the graph, even small
changes in the number of links to VO blocks has a significant impact on
reliability, while even a 50 times increase in the VC block link counts only
slightly affects VC reliability.  The key factor placed is that  $N_1 +N_2 <
N_o$, caused by the fact that the VM-centric approach localizes deduplication
and packs  data blocks for one VM as much as possible.  The extra replicaton
for PDS blocks also signficantly increases the snapshot availability even when
a PDS file block is shared by every VM.

% while in VO even small increases in $L$ causes a large decrease in availability. 
Figure~\ref{fig:pds-replication}
shows the advantages of increasing the replication factor for PDS blocks. the
numbers in the graph are only meant to be relative, as we assume higher PDS
block links than we have measured in our dataset (to account for a much larger
body of data). It is easy to see though that increasing the replication of just
the PDS blocks (which are the most popular blocks) can have a positive impact
on the overall reliablity of the VM backups. These figures together show the
advantages of the VM-centric model, and the advantages that separating the
replication factor for popular blocks can have on reliability.

\begin{figure}[htbp]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
                cycle multi list={
                    mline\nextlist
                    [2 of]mmark*\nextlist
                },
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                %reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
                \addlegendentry{$VC\,20$ (measured)}
                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
                \addlegendentry{$VC\,2500$ (worst-case)}
                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
                \addlegendentry{$VO\,5$ (measured)}
                \addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
                \addlegendentry{$VO\,20$ (optimistic)}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail for VO and VC models for
  varying degrees of block sharing (i.e. average number of VMs that use a
  block). Non-PDS replication fixed at 3 and PDS replication increased to 4.
  Graph shown for 100 machine cluster.
  }
  \label{fig:vm-availability}
\end{figure}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 1000)}
  \label{fig:pds-replication}
\end{figure}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		%extra y ticks={99.99}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication2.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication2.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication2.txt};
                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication2.txt};
                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 20)}
  \label{fig:pds-replication2}
\end{figure}
